### 2024-10-24 paper/1-intro.tex
Write the intro in bullet points

>>>>

\begin{itemize}
\item Wasm
  \begin{itemize}
  \item is low-level bytecode language, platform-indep, ...
  \item is compile target for Web applications
  \item is used in wide area such as IoT, ...
  \end{itemize}
\item Wasm Spec
  \begin{itemize}
  \item descibes syntax and semantics of Wasm
  \item should be rigorous because ... (brief explanation for two format)
  \item has two format to describe semantics (formal\&prose notation)
  \item formal notation is written in math expression: concise, clear, amenable to proofs, ...
  \item prose notation is step by step instruction written English: vague (in some part), amenable to developing engines
  \end{itemize}
\item SpecTec
  \begin{itemize}
  \item is proposed to alleviate spec writing process
  \item is accepted by Wasm committee to be an official Wasm specification tool
  \item define AL to describe Wasm semantics in prose notation
  \item AL is designed to be similar to prose notation (describe with fig)
  \item implement AL interpreter to make the spec executable
  \item executable spec passes official wasm test $\leftarrow$ correctness
  \end{itemize}
\item Problem
  \begin{itemize}
  \item no semantics in AL
  \item prose notation is still vague unless read AL interpreter code
  \item ???
  \end{itemize}
\item Contribution
  \begin{itemize}
  \item formalize AL syntax$\&$semantics
  \item make prose notation clear to understand
  \item ???
  \end{itemize}
\end{itemize}
